preciseTAD: A machine learning framework for precise TAD boundary prediction at base pair resolution

### 2020-07-23 Manuscript/manuscript.Rmd
Discuss different TAD boundary types

Another limitation of *preciseTAD* is that it does not provide information about hierarchy of TAD boundaries, but instead provides the coordinates of boundary points and regions. Studies have shown evidence of the hierarchical nature to the 3D architecture of the human genome [@hansen2018recent; @weinreb2016identification; @fraser2015hierarchical]. In such a hierarchy, the boundaries provided by *preciseTAD* can be interpreted as the lowest level of boundaries [??? This can be debated. We are training on and predicting certain level of boundaries. Suggesting discussing that false positives detected by preciseTAD may represent boundaries at finer resolution].

>>>>

Another limitation of *preciseTAD* is that it does not distinguish boundary types. The hierarchical nature of TAD boundaries [@weinreb2016identification; @fraser2015hierarchical; @Cresswell:2020ab] is not considered by *preciseTAD* due to the lack of gold standard of TAD hierarchy. Recent research distinguishes CTCF-associated boundaries, CTCF-negative YY1-enriched boundaries, CTCF- and YY1- depleted promoter boundaries, and a fourth class of weak boundaries largely depleted of all three features [@Krietenstein:2020aa]. Furthermore, actively transcribed regions can serve as TAD boundaries themselves, independently of CTCF binding [@Harrold:2020aa]. This may lead to high proportion of TAD boundaries being undetected by *preciseTAD* despite being detected by TAD callers [??? What is the false positive rate? We may be missing TADs that are distinct from the canonical CTCF boundaries. TBD]. Our future work will include defining separate models trained on different TAD boundary types, and predicting precise locations for each of them.
